Fast and exact visibility on digitized shapes and application to feature-aware normal estimation and pattern detection

### 2025-03-20 DGMM2025/paper.tex
Skeleton of paper
Figures and visibility definition

\usepackage{changes}
\setauthormarkup{}
\definechangesauthor[name=jo, color=magenta]{JO}
\definechangesauthor[name=rom, color=teal]{ROM}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

>>>>

\usepackage{changes}
\usepackage{amstex}
\setauthormarkup{}
\definechangesauthor[name=jo, color=magenta]{JO}
\definechangesauthor[name=rom, color=teal]{ROM}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Visibility through tangency of chords}

    Introduce full convexity and tangency. \cite{lachaud:2021-dgmm,lachaud:2022-jmiv}.

    \begin{definition}
        Two points \( p \) and \( q \) on \( K \) are visible if and only if the segment \([p, q]\) is included in \(\text{Star}(K)\), i.e., [p, q] \subseteq \text{Star}(K)\).
    \end{definition}

    % Examples of visibility in 2D
    \begin{figure}
        \centering
        \begin{tikzpicture}
            \draw[dashed] (0,0) -- (4,2);
            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p1};
            \filldraw[black] (4,2) circle (0.05) node[anchor=north] {q1};
            \draw (0,0) -- (1,0) -- (2,0) -- (2,1) -- (3,1) -- (3,2) -- (4,2);
            \draw[dashed=gray] (-1,0) -- (-1,1) -- (0,1) -- (1,1) -- (1,2) -- (2,2) -- (2,3) -- (3,3) -- (4,3) -- (5,3) -- (5,2) -- (5,1) -- (4,1) -- (4,0) -- (3,0) -- (3,-1) -- (2,-1) -- (1,-1) -- (0,-1) -- (-1,-1) -- (-1,0);
        \end{tikzpicture}
        \hspace{\floatsep}
        \begin{tikzpicture}
            \draw[red,dashed] (0,0) -- (3,2);
            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p2};
            \filldraw[black] (3,2) circle (0.05) node[anchor=north] {q2};
            \draw (0,0) -- (0,1) -- (0,2) -- (1,2) -- (1,3) -- (2,3) -- (2,2) -- (3,2);
            \draw[dashed=gray] (-1,0) -- (-1,1) -- (-1,2) -- (-1,3) -- (0,3) -- (0,4) -- (1,4) -- (2,4) -- (3,4) -- (3,3) -- (4,3) -- (4,2) -- (4,1) -- (3,1) -- (2,1) -- (1,1) -- (1,0) -- (1,-1) -- (0,-1) -- (-1,-1) -- (-1,0);
        \end{tikzpicture}
        \newline
        \newline
        \begin{tikzpicture}
            \draw[red,dashed] (0,0) -- (2,0);
            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p3};
            \filldraw[black] (2,0) circle (0.05) node[anchor=north] {q3};
            \draw (0,0) -- (0,1) -- (0,2) -- (1,2) -- (2,2) -- (2,1) -- (2,0);
            \draw[dashed=gray] (-1,-1) -- (-1,3) -- (3,3) -- (3,-1) -- (1,-1) -- (1,1) -- (1,-1) -- (-1,-1);
        \end{tikzpicture}
        \hspace{\floatsep}
        \begin{tikzpicture}
            \draw[red,dashed] (0,0) -- (2,2);
            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p4};
            \filldraw[black] (2,2) circle (0.05) node[anchor=north] {q4};
            \draw (0,0) -- (0,1) -- (0,2) -- (1,2) -- (2,2);
            \draw[dashed=gray] (-1,0) -- (-1,1) -- (-1,2) -- (-1,3) -- (0,3) -- (1,3) -- (2,3) -- (3,3) -- (3,2) -- (3,1) -- (2,1) -- (1,1) -- (1,0) -- (1,-1) -- (0,-1) -- (-1,-1) -- (-1,0);
        \end{tikzpicture}
        \caption{Examples of visibility in 2D, only q1 is visible from p1, q2 is not visible from p2 (gets out of the star), q3 is not visible from p3 (gets out of the star from a 1-d cell), q4 is not visible from p4 (gets out of the star from a 0-d cell).}
        \label{fig:visibility-2d}
    \end{figure}

    % Example of visibility not necessarily connected
    % Path from p to q : r u r u r r r r r u r
    \begin{figure}
        \centering
        \begin{tikzpicture}
            \draw (0,0) -- (1,0) -- (1,1) -- (2,1) -- (2,2) -- (3,2) -- (4,2) -- (5,2) -- (6,2) -- (7,2) -- (7,3);
            \draw [black, dashed] (0,0) -- (7,3);
            \draw [red, dashed] (0,0) -- (7,2);
            \draw [red, dashed] (0,0) -- (6,2);
            \filldraw[black] (0,0) circle (0.05) node[anchor=north] {p};
            \filldraw[gray] (1,0) circle (0.05);
            \filldraw[gray] (1,1) circle (0.05);
            \filldraw[gray] (2,1) circle (0.05);
            \filldraw[gray] (2,2) circle (0.05);
            \filldraw[gray] (3,2) circle (0.05);
            \filldraw[gray] (4,2) circle (0.05);
            \filldraw[gray] (5,2) circle (0.05);
            \filldraw[red] (6,2) circle (0.05);
            \filldraw[red] (7,2) circle (0.05);
            \filldraw[black] (7,3) circle (0.05) node[anchor=west] {q};
            \draw[dashed=gray] (-1,-1) -- (-1,1) -- (0,1) -- (0,2) -- (1,2) -- (1,3) -- (6,3) -- (6,4) -- (8,4) -- (8,1) -- (3,1) -- (3,0) -- (2,0) -- (2,-1) -- (-1,-1);
        \end{tikzpicture}
        \caption{Example of non connex visibility in 2D, q is visible from p while the visibility points are not 26-connected.}
        \label{fig:visibility-2d-not-connected}
    \end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Fast computation using integer intervals intersections}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Feature-aware normal estimation on digital surfaces}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{credits}
        \subsubsection{\ackname}
        This work is partially supported by the French National Research Agency
        within the StableProxies project (ANR-22-CE46-0006).
%% \subsubsection{\discintname}
%% It is now necessary to declare any competing interests or to specifically
%% state that the authors have no competing interests. Please place the
%% statement with a bold run-in heading in small font size beneath the
%% (optional) acknowledgments\footnote{If EquinOCS, our proceedings submission
%% system, is used, then the disclaimer can be provided directly in the system.},
%% for example: The authors have no competing interests to declare that are
%% relevant to the content of this article. Or: Author A has received research
%% grants from Company W. Author B has received a speaker honorarium from
%% Company X and owns stock in Company Y. Author C is a member of committee Z.
    \end{credits}
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
    \bibliographystyle{splncs04}
    \bibliography{biblio}
